### 2018-06-26 latex/results.tex

It is interesting to note that without NNMT, NAD concentration and consumption flux are both considerably affected by cell division rates, at least if the enzyme expression is kept constant. This is, of course, an artificial scenario, as one would assume organisms to regulate enzyme expression to achieve similar levels of metabolite concentrations instead. However, there seems to be an apparent trade off between maintainable NAD concentration and consumption flux in the absence of NNMT. In contrast, NAD consumption rates increase with NAD concentration in the presence of NNMT and both are relatively independent of cell division rates. \todo{The last sentence is unclear to me. Consumption increases with concentration? That is not in the figure. I needed to read often to understand what "NNMT and both" means.}

@@

From these observations, we derived two possible hypotheses regarding the role of the loop for NamPRT function. Firstly, we analysed whether the deletion of the amino acids 42 to 51 has an effect on the localisation of the human enzyme. We thus performed immunofluorescence imaging with FLAG-tagged proteins, but both wildtype and mutant protein showed a mixed cytosolic nuclear localisation (fig.~\ref{fig:unresolved_loop}C). We therefore conclude that the partial nuclear localisation of NamPRT is not affected by the sequence deletion\todo{As there are other NLS in the protein, this one could just be non-functional also with loop, couldn’t it?}.

>>>>

It is interesting to note that without NNMT, NAD concentration and consumption flux are both considerably affected by cell division rates, at least if the enzyme expression is kept constant. This is, of course, an artificial scenario, as one would assume organisms to regulate enzyme expression to achieve similar levels of metabolite concentrations instead. However, there seems to be an apparent trade off between maintainable NAD concentration and consumption flux in the absence of NNMT. In contrast,  in the presence of NNMT NAD consumption rates increase with NAD concentration and both are relatively independent of cell division rates. \todo{The last sentence is unclear to me. Consumption increases with concentration? That is not in the figure. I needed to read often to understand what "NNMT and both" means.}

@@

From these observations, we derived two possible hypotheses regarding the role of the loop for NamPRT function. Firstly, we analysed whether the deletion of the amino acids 42 to 51 has an effect on the localisation of the human enzyme. We thus performed immunofluorescence imaging with FLAG-tagged proteins, but both wildtype and mutant protein showed a mixed cytosolic nuclear localisation (fig.~\ref{fig:unresolved_loop}C). We therefore conclude that the partial nuclear localisation of NamPRT is not affected by the sequence deletion.
